Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-02-13 hpmoon-asoco.tex
Made some improvements to explanation of figures

With respect to the average
number of solutions per front, there is a clear difference 
 with the baseline with $L=512$, where this value is in the most
of the cases, less than a half. The number of non-dominated solutions
also implies a better Spread indicator, where the baseline 
 obtains better (or not significantly different) values in the majority of the compared configurations.

@@

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048}, showing the final PFs of one arbitrary sample run of each combination. These figures allow visualizing the effect of the different chromosome sizes and number of islands in each different benchmark. The first one, ZDT1, has a convex Pareto-optimal front. Comparing results from $L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) it is apparent that the quality of the generated PFs depends on the chromosome size. Specifically, with $L=512$ it can be seen that the PFs quality decreases in Spread and HV with all configurations, but the SLA methods behave worse than $B$, as it also was shown on average in Table \ref{tab:results512}. Nevertheless, if we focus on the plots obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this difference is less clear. It can be seen in Figure \ref{fig:plot_zdt1_2048} that solutions obtained by the SLA methods are more dispersed than the baseline as $P$ grows. However, with $A$, the area covered by the PF is still larger.

%ZDT2
ZDT2 has a non-convex Pareto front. From Figures \ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.  Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.

>>>>

With respect to the average
number of solutions per front, there is a clear difference 
 with the baseline with $L=512$, where this value is in most
cases, less than a half. The number of non-dominated solutions
also implies a better Spread indicator, where the baseline 
 obtains better (or not significantly different) values in the majority of the compared configurations.

@@

%%%%%%FERGU: WARNING, THIS SECTION IS STILL SHIT
%ZDT1 
After establishing the performance of the new method and in order to
have some insight on how they work, let's check the effect of the different chromosome sizes and number of
islands. Figures \ref{fig:plot_zdt1_512} to \ref{fig:plot_zdt6_2048} show the
final PFs of one arbitrary sample run of each combination;. The first
one, ZDT1, has a convex Pareto-optimal front. Comparing results from
$L=512$ (Figure \ref{fig:plot_zdt1_512}) and $L=2048$ (Figure
\ref{fig:plot_zdt1_2048}) it is apparent that the quality of the
generated PFs depends on the chromosome size. Specifically, all
configurations  with
$L=512$  seem to have a worse Spread and HV, on the other hand, the
SLA methods behave worse than $B$, as it was also shown on average in
Table \ref{tab:results512}. Nevertheless, if we focus on the plots
obtained with $L=2048$ (Figure \ref{fig:plot_zdt1_2048}) this
difference is less clear. Figure \ref{fig:plot_zdt1_2048} shows that
solutions obtained by the SLA methods show higher dispersion than the
baseline as $P$ grows. However, with $A$, the area covered by the PF
is still larger.

%ZDT2
ZDT2 has a non-convex Pareto front. From Figures
\ref{fig:plot_zdt2_512} and \ref{fig:plot_zdt2_2048} it is clear that, as in the previous problem ZDT1, there is a decrease of quality for all configurations as the size of $P$ increases.  Nevertheless, for this benchmark, there is not a clear decrease in the PF quality when $L$ goes from 512 to 2048.
